Implementing DNS in C0

### 2017-11-17 proposal.tex
update outline
add Farzaneh's contribution

Jon

@@

Farzaneh.

@@

\nocite{willsey-prabhu-pfenning:2016, rfc:1034, rfc:1035}
\bibliographystyle{abbrv}
\bibliography{bibtex-references/refs,project}

>>>>

Who will write this? I can write some, but I don't really know very much. -Jon

@@

The \Kwd{C0} programming language is a restricted subset of \Kwd{C}
that provides implicit memory safety to
programmers~\cite{pfenning:c0-reference}. Restrictions on pointer
arithmetic and casting, for example, allow the language to detect and
prevent any attempt to access an array out of its bounds. Furthermore,
there is no need for error-prone manual memory management, since
\Kwd{C0} is itself garbage-collected. Further safety conditions can be
enforced with contracts, which are a class of assertions including
loop invariants, pre- and post-conditions, and dynamically checkable
correctness conditions for programs.

\Kwd{Concurrent C0} (\Kwd{CC0}) is an extension of \Kwd{C0} that
offers concurrency based on message passing by providing processes as
the units of concurrent execution and channels as their message
buffers~\cite{willsey-prabhu-pfenning:2016}. Concurrent processes
communicate over channels using a protocol that is disciplined by
session types~\cite{caires-pfenning-toninho:2013,
  balzer-pfenning:2017}. In this protocol, each channel is typed such
that it can either send or receive a message and, thus, it
deliberately models the client/provider relation.

However, the protocol is also able to characterize processes that are
not completely sequential, and branch into different sequences as they
encounter choices. This typing system, also, guarantees that data is
send and received in the correct order and by the correct processes
(session fidelity), and that the communication is always one-to-one.
The \Kwd{CC0} programming language is secure in terms of both memory
and communication safety.

@@

\nocite{rfc:1034, rfc:1035}
\bibliographystyle{abbrv}
\bibliography{bibtex-references/refs,project}
